Higgs Assisted Razor Search for Higgsinos at a 100 TeV $pp$ Collider

### 2019-12-17 main.tex
Added ratios of xsections of generated bg events to 3ab-1 at 100 TeV pp collider

Table \ref{tab:cc_cutflowtable} shows the cut efficiencies for a representative
signal benchmark point with $\mu =$ 1 TeV and $M_1$ = 25 GeV.   The
cross-sections of the backgrounds are obtained from MadEvent after performing
the MLM matching procedure. Their small size reflects the $m_{\ell\ell}$ and
$\slashed{E}_T$ cuts we imposed at the parton level. For all the benchmark
points, we require a minimum of three background events (at the MC level, i.e.
unweighted) left over after cuts\footnote{\ap{This is inspired by the upper
    one-sided limit for the mean of a Poisson variable given zero observed
    events, for a confidence level of 95\% (see Table 39.3 of
    \cite{PhysRevD.98.030001}), however, it does not reflect it exactly (since
    we required a minimum on unweighted rather than weighted events).  We
    observed that as we generated more unweighted background events, the
    discovery reach of our analysis showed a steady increase. This, combined with the
    fact that we were pushing the limits of our storage and computing capacity
    (we generated $\approx 14$ million $tt$ events and $\approx
    850$K $tbW$ events - both unweighted), lead us to believe that the projected reaches
presented in this paper are conservative ones.}}. We can see that, after
applying our cuts, $tbW$ remains as the dominant backgrounds, followed by $tt$.
The values of the razor variable cuts were chosen to maximize the significance,
$S/\sqrt{B}$ (calculated for an integrated luminosity of 3000 fb$^{-1}$), shown
in the last column.

>>>>

Table \ref{tab:cc_cutflowtable} shows the cut efficiencies for a representative
signal benchmark point with $\mu =$ 1 TeV and $M_1$ = 25 GeV.   The
cross-sections of the backgrounds are obtained from MadEvent after performing
the MLM matching procedure. Their small size reflects the $m_{\ell\ell}$ and
$\slashed{E}_T$ cuts we imposed at the parton level. For all the benchmark
points, we require a minimum of three background events (at the MC level, i.e.
unweighted) left over after cuts\footnote{\ap{This is inspired by the upper
    one-sided limit for the mean of a Poisson variable given zero observed
    events, for a confidence level of 95\% (see Table 39.3 of
    \cite{PhysRevD.98.030001}), however, it does not reflect it exactly (since
    we required a minimum on unweighted rather than weighted events).  We
    observed that as we generated more unweighted background events, the
    discovery reach of our analysis showed a steady increase. This, combined
    with the fact that we were pushing the limits of our storage and computing
    capacity (we generated $\approx 10$ million $tt$ events, $\approx 26$
    million $tbW$  events and $100$K $bbWW$ events - all unweighted), lead us
    to believe that the projected reaches presented in this paper are
conservative ones. The ratio of the cross section of the generated events to
that expected at a 100 TeV $pp$ collider with 3 ab$^{-1}$ is $\approx 0.2$ for
$tt$, 0.05 for $tbW$, $0.46$ for $bbWW$}}. We can see that, after applying our
cuts, $tbW$ remains as the dominant backgrounds, followed by $tt$.  The values
of the razor variable cuts were chosen to maximize the significance,
$S/\sqrt{B}$ (calculated for an integrated luminosity of 3000 fb$^{-1}$), shown
in the last column.
